Nesterov's First Order Method Accelerations: Unifications, Applications and Numerical Experiments

### 2025-03-01 Notebook LaTEX/Proposal/presentation.tex
=w=, no comments
>w<, changes

% SLIDE INFORMATION ============================================================
\author{Hongda Li}
\title[Thesis Proposal Talk]{Nesterov's First Order Method Accelerations: Unifications, Applications  and Numerial Experiments}
% \newcommand{\email}{lalala@lala.la}
\institute[UBCO]{
    University of British Columbia Okanagan
}
\date{\today}
\subject{Nesterov's acceleration and its applications}

@@

        Part I: Introduction. 

@@

                \item Introducing the Catalyst metal acceleration framework. 

@@

                \item It demonstrates crucial ideas on convergence analysis involving nexact evaluation of proximal point method under the the convex settings. 

@@

\section{Contents of the draft paper}
    \begin{frame}{Contents of our draft papers}
        Part II: Contents of our current draft paper. 
        \begin{block}{Upcoming contents}
            We explain results from our relaxed, weak accelerated proximal gradient (R-WAPG). 
            \begin{enumerate}
                \item The R-WAPG sequence and the method of R-WAPG. 
                \item A generic convergence theorem of R-WAPG. 
                \item Three equivalent forms of R-WAPG. 
                \item Specialized convergence results with for specific instances of FISTA variants in the literatures. 
                \item A parameter free formulation of R-WAPG and the results of our preliminary numerical experiments. 
                \item Nesterov's idea of strong convexity transfer and the R-WAPG framework. 
            \end{enumerate}
        \end{block}

@@

                        g_k &= \mathcal G_L y_k, 

@@

                        (\gamma_k(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k), 

@@

@@

                            v_{k + 1} + 

@@

@@

            To the best of our knowledge, the last variant is, and we have the convergence claim for it using R-WAPG. 

@@

                    \STATE{$\mu_k := D_f(y_{k + 1}, y_{k})/\Vert y_{k + 1} - y_k\Vert^2 + (1/2)\mu_k$;}

@@

                \includegraphics[width=0.64\textwidth]{assets/simple_regression_loss_sc_estimates_1024.png}
                \caption{$N = 1024$, the $\mu$ estimates produced by Algorithm \ref{alg:free-rwapg} (R-WAPG) is recorded. }

@@

            There is one detail that our R-WAPG doesn't incorporate on all Euclidean variants of FISTA. 

>>>>

% SLIDE INFORMATION ============================================================
\author{Hongda Li}
\title[Thesis Proposal Talk]{Nesterov's First Order Method Accelerations: Unifications, Applications and Numerical Experiments}
% \newcommand{\email}{lalala@lala.la}
\institute[UBCO]{
    University of British Columbia Okanagan
}
\date{\today}
\subject{Nesterov's acceleration and its applications}

@@

        Part I: Introduction to Relaxed Weak Accelerated Proximal Gradient (R-WAPG). 

@@

                \item Introducing the Catalyst meta acceleration framework. 

@@

                \item It demonstrates crucial ideas on convergence analysis involving inexact evaluation of proximal point method under the convex settings. 

@@

\section{Contents of the draft paper}
    \begin{frame}{Contents of our draft papers}
        Part II: Contents of our current draft paper. 
        \begin{block}{Upcoming contents}
            We explain results from our draft paper on relaxed, weak accelerated proximal gradient (R-WAPG). 
                \item The R-WAPG sequence and the method of R-WAPG.
                \item A generic convergence theorem of R-WAPG. 
                \item Three equivalent forms of R-WAPG. 
                \item Specialized convergence results of Euclidean FISTA variants in the literatures. 
                \item A parameter free formulation of R-WAPG and the results of our preliminary numerical experiments. 
                \item Nesterov's idea of strong convexity transfer and the R-WAPG framework. 

@@

                        % g_k &= , 

@@

                        (\gamma_k(1 - \alpha_k) v_k - \alpha_k \mathcal G_L y_k + \mu \alpha_k y_k), 

@@

            \eqref{eqn:lower-linearization} Comes from Lemma \ref{thm:prox-grad-ineq}. 

@@

                            v_{k} + 

@@

                \hspace{-1em}
                    Constant\\ Momentum

@@

            To the best of our knowledge, the last variant is new, and we have the convergence claim for it using R-WAPG. 

@@

                    \STATE{$\mu_{k + 1} := D_f(y_{k + 1}, y_{k})/\Vert y_{k + 1} - y_k\Vert^2 + (1/2)\mu_k$;}

@@

                    \includegraphics[width=\textwidth]{assets/simple_regression_loss_sc_estimates_1024.png}
                    \includegraphics[width=\textwidth]{assets/simple_regression_loss_1024.png}
                    $N = 1024$, the $\mu$ estimates produced by Algorithm \ref{alg:free-rwapg} (R-WAPG) is recorded.

@@

            There is one detail in the literatures that our R-WAPG doesn't incorporate.  
